---
title: "Goggles experiment - analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

source("./functions/diagnostic_fcns.r")
source("./functions/glmm_stability.r")
source("./functions/boot_glmm2.r")
source("./functions/glmmTMB_stability.r")
source("./functions/drop1_para_glmmtmb.r")
source("./functions/extract_ranef_gmmTMB.r")


load(file="goggles_workspace.RData")
```

Yuna: trial 3 repeated due to a noise outside --> trial repeated
Alou: to be excluded (exceeds planned sample size)

## Read in data

```{r}
remove<-c("Lakota", 	"Minos",	"Cully",	"Eowyn",	"Amarie",	"Ambiano",	"Winnie2",	 "Alou")#dogs that did not meet inclusion criteria 

demo.data<-read.csv(file = "data/Goggles_Counterbalance_ filled.csv")%>%
  rename(Subject="dog_name")%>%
  filter(!Subject %in% remove)%>% 
  mutate(transparent_side=ifelse(tunnel_right_side==transparent_screen, "right", "left"))%>%
  mutate(looking_condition=ifelse(tunnel_right_side=="blue"& transparent_screen=="blue"& looking_direction=="R", "transparent",
                                  ifelse(tunnel_right_side=="yellow"& transparent_screen=="yellow"& looking_direction=="R", "transparent",
                                         ifelse(tunnel_right_side=="blue"& transparent_screen=="yellow"& looking_direction=="L", "transparent",
                                  ifelse(tunnel_right_side=="yellow"& transparent_screen=="blue"& looking_direction=="L", "transparent","opaque"
                                  )))))

raw.data<-read.csv(file="data/scoringproject_50_Goggles_experiment.csv")%>%
  filter(!Subject %in% remove)


levels(as.factor(raw.data$Subject))
levels(as.factor(demo.data$Subject))
table(raw.data$Subject, raw.data$trial)

raw.data%>%filter(is.na(trial))

```
### Manipulation check
```{r}
raw.data.man.check<-read.csv(file="data/scoringproject_50_Goggles_experiment.csv")%>%
  filter(!Subject %in% remove) %>% 
  filter(Behaviour== "Manipulation check ")
str(raw.data.man.check)

#first chosen screen
raw.data.man.check.wider<-raw.data.man.check %>% 
  dplyr::select(Subject, Value, Start, Stop, duration) %>% 
  pivot_wider(names_from = Value, values_from = Start) %>% 
  rename("start_transparent" = "Manipulation check transparent") %>% 
  rename("start_opaque" = "Manipulation check opaque")

raw.data.man.check.wider.agg<-raw.data.man.check.wider %>% 
  group_by(Subject) %>% 
  summarise(min_transparent=min(start_transparent, na.rm=T),
            min_opaque=min(start_opaque, na.rm=T)) %>% 
  mutate(min_opaque=recode(as.factor(min_opaque), "Inf"= NA))
levels(as.factor(raw.data.man.check.wider.agg$min_opaque))                           
#replace "Inf" with NA (meaning the dogs never approached the opaque tunnel)          
raw.data.man.check.wider.agg$min_opaque[(raw.data.man.check.wider.agg$min_opaque=="Inf")] <- "NA"

raw.data.man.check.wider.agg<-raw.data.man.check.wider.agg %>% 
  mutate(transp_chosen_first=ifelse((min_transparent<min_opaque)|is.na(min_opaque),1,0))

binom.test(sum(raw.data.man.check.wider.agg$transp_chosen_first), length(raw.data.man.check.wider.agg$transp_chosen_first))
#more dogs than expected by chance (28/32) approached and looked through the transparent screen first on the trial in which they passed (could be first or second) (p = 1.93e-05) 

binom.test(23,32) #dogs that approached the transparent screen first on their first man. check trial, out of the 32 tested dogs
#p-value = 0.020

#if we consider the additional 5 dogs that did not pass the manipulation check, the result holds:
#dogs that approached the transparent screen first on the trial in which they passed (could be first or second) the manipulation check:
binom.test(28,37) #p-value = 0.003
```


## Aggregating data per trial

### First look
```{r}
first_look_data<-raw.data%>%
  filter(Behaviour=="First look")%>%
  filter(!is.na(trial))%>%
  group_by(Subject, trial, Behaviour, Value)%>%
  summarise(first_look_transparent=sum(Value=="First look transparent"))%>%
  ungroup()%>%
  inner_join(demo.data)%>%
  mutate(first_look_cong=as.numeric(ifelse(first_look_transparent==1 & looking_condition=="transparent", 1, 
                                           ifelse(first_look_transparent==0 & looking_condition=="opaque", 1, 0))))%>%
  mutate(looking_score=as.numeric(ifelse(first_look_cong==0, -1, first_look_cong)))

table(first_look_data$Subject, first_look_data$trial)
```



```{r}
#descriptive stats
mean(first_look_data$first_look_cong) #probability that dogs directed their first look to the gaze-congruent side of the room
# 0.60
#SE
sd(first_look_data$first_look_cong)/sqrt(length(first_look_data$first_look_cong))
#0.05

#t.test
first_looks_data_descr<-first_look_data%>%
  group_by(Subject)%>%
  summarise(mean_first_look_cong=mean(first_look_cong, na.rm=TRUE), mean_first_look_transparent=mean(first_look_transparent),
            se_first_look_con=sd(first_look_cong, na.rm=TRUE)/sqrt(length(first_look_cong)))

t.test(first_looks_data_descr$mean_first_look_cong, mu=0.5) 
#t = 2.7519, df = 31, p-value = 0.009809
#dogs are more likely than chance to direct their first look to the gaze-congruent side of the room

     
##Plot first looks congruent
first_looks_data<-first_look_data%>%
  group_by(Subject, looking_condition)%>%
  summarise(mean_first_look_cong=mean(first_look_cong), mean_first_look_transparent=mean(first_look_transparent),
se_first_look_con=sd(first_look_cong, na.rm=TRUE)/sqrt(length(first_look_cong))
            )%>%
  ungroup()%>%
  complete(Subject, looking_condition, fill=list(mean_first_look_cong=0)) %>%  #fill in 0s
  # complete(Subject, looking_condition, fill=list(mean_first_look_transparent=0)) %>% #fill in 0s
  # complete(Subject, looking_condition, fill=list(se_first_look_con=0)) #fill in 0s

  table(first_looks_data$Subject, first_looks_data$looking_condition)

first_looks_data_agg<-first_looks_data%>%
  group_by(looking_condition)%>%
  summarise(mean_fl_con=mean(mean_first_look_cong, na.rm=TRUE), se_fl_con=sd(mean_first_look_cong, na.rm=TRUE)/sqrt(length(mean_first_look_cong)), mean_fl_trans=mean(mean_first_look_transparent, na.rm=TRUE), se_fl_trans=sd(mean_first_look_transparent, na.rm=TRUE)/sqrt(length(mean_first_look_transparent)))

plot_first_look<-ggplot(data=first_looks_data_agg, aes(x=looking_condition, y=mean_fl_con))+
  geom_bar(stat="identity", alpha=0.8)+
  geom_errorbar(aes(ymin=mean_fl_con-se_fl_trans, ymax=mean_fl_con+se_fl_trans), width=0.5)+
  #scale_y_continuous(breaks = seq(0,0.75, by=0.25))+
  ylim(0, 0.85)+
  xlab("Experimenter gaze cue")+
  ylab("Proportion first look at gaze congruent target")+
  geom_hline(lty=2, yintercept=0.5)+
  theme_classic()

plot_first_look
```


```{r}
ggsave(plot_first_look, filename = "graphics/LL_first_look.png", width=5, height=6, scale=0.6)
```

first look transparent plot
```{r}
p_flt<-ggplot(data=looking_score_data_agg, aes(x=looking_condition, y=mean_fl_trans))+
  geom_bar(stat="identity")+
  geom_hline(yintercept = 0.5, lty=3, lwd=1, color="grey")+
  geom_errorbar(aes(ymin=mean_fl_trans-se_fl_trans, ymax=mean_fl_trans+se_fl_trans), width=0.5)+
  xlab("Experimenter gaze cue")+
  ylab("First look to transparent tunnel")+
  theme_classic()+
  ylim(0, 0.8)

p_flt
```


### First choice
```{r}
first_choice_data<-raw.data%>%
  filter(Behaviour=="First target choice")%>%
  filter(!is.na(trial))%>%
  group_by(Subject, trial, Behaviour, Value)%>%
  summarise(first_choice_transparent=sum(Value=="First choice transparent"))%>%
  ungroup()%>%
  inner_join(demo.data)%>%
  mutate(first_choice_cong=as.numeric(ifelse(first_choice_transparent==1 & looking_condition=="transparent", 1, 
                                           ifelse(first_choice_transparent==0 & looking_condition=="opaque", 1, 0))))
  
```

Aggregate first choice by subject and condition
```{r}
first_choice_agg<-first_choice_data%>%
  group_by(Subject, looking_condition)%>%
  summarise(mean_choice=mean(first_choice_cong))

first_choice_agg_subj<-first_choice_data%>%
  group_by(Subject)%>%
  summarise(mean_choice=mean(first_choice_cong),
            se_choice=sd(first_choice_cong)/sqrt(length(first_choice_cong)))

mean(first_choice_agg_subj$mean_choice)
sd(first_choice_agg_subj$mean_choice)/sqrt(length(first_choice_agg_subj$mean_choice))
#on average dogs chose the gaze-congruent bucket on 56% of trials (SE:3%)

t.test(first_choice_agg_subj$mean_choice, mu=0.5) #t = 2.0203, df = 31, p-value = 0.05206

#adjust first choice and first look p-values for multiple comparisons
library(broom)
p.adjust(c(0.009809,0.05206), method = "bonferroni", n = 2)
#0.019618, 0.104120

first_choice_agg2<-first_choice_agg%>%
  group_by(looking_condition)%>%
  summarise(mean=mean(mean_choice), se=sd(mean_choice)/sqrt(length(mean_choice)))
```
```{r}
p_choice<-ggplot(data=first_choice_agg2, aes(x=looking_condition, y=mean))+
  geom_bar(stat="identity", alpha=0.8)+
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=0.5)+
  geom_hline(yintercept = 0.5, lty=2)+
  ylim(0,0.85)+
  xlab("Experimenter gaze cue")+
  ylab("Proportion choice of gaze congruent target")+
  theme_classic()

p_choice
```


```{r}
ggsave(p_choice, filename = "graphics/LL_first_choice.png", width=5, height=6, scale=0.6)
```

###Figure 4: plot of first looks and first choices
```{r}
library(cowplot)
fl_fc_plot<-plot_grid(plot_first_look, p_choice, nrow=1, labels=c("A)", "B)"))
fl_fc_plot
```
```{r}
ggsave(fl_fc_plot, filename = "graphics/LL_first_look&choice.png", width=9, height=7, scale=0.6)
```

### Inspection behind screen
```{r}
inspection_data<-raw.data%>%
  filter(Behaviour=="Inspection behind screen")%>%
  filter(!is.na(trial))%>%
  group_by(Subject, trial, Behaviour, Value)%>%
  summarise(inspection_transparent=sum(Value=="Inspection behind transparent"), inspection_opaque=sum(Value=="Inspection behind opaque"))%>%
  ungroup()%>%
  inner_join(demo.data)%>%
  mutate(inspection_cong=as.numeric(ifelse(inspection_transparent==1 & looking_condition=="transparent", 1, 
                                           ifelse(inspection_transparent==0 & looking_condition=="opaque", 1, 0))))


inspection_data_complete<-raw.data%>%
  filter(Behaviour=="Inspection behind screen")%>%
  filter(!is.na(trial))%>%
  group_by(Subject, trial)%>%
  summarise(inspection_opaque=sum(Value=="Inspection behind opaque"))%>%
  ungroup()%>%
  full_join(demo.data)%>%
  complete(Subject, trial,  fill=list(inspection_opaque=0)) #fill in 0s


length(unique(inspection_data_complete$Subject))  
```
Aggregate inspection by subject and condition
```{r}
inspection_agg<-inspection_data%>%
  group_by(Subject, looking_condition)%>%
  summarise(mean_inspection=mean(inspection_opaque))

inspection_agg2<-inspection_agg%>%
  group_by(looking_condition)%>%
  summarise(mean=mean(mean_inspection), se=sd(mean_inspection)/sqrt(length(mean_inspection)))


inspection_agg_complete<-inspection_data_complete%>%
  group_by(Subject, looking_condition)%>%
  summarise(mean_inspection=mean(inspection_opaque))

inspection_agg_complete2<-inspection_agg_complete%>%
  group_by(looking_condition)%>%
  summarise(mean=mean(mean_inspection), se=sd(mean_inspection)/sqrt(length(mean_inspection)))
```

### Plot of inspection behind barrier 
```{r}
p_inspection_complete<-ggplot(data=inspection_agg_complete2, aes(x=looking_condition, y=mean))+
  geom_bar(stat="identity")+
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=0.5)+
  xlab("Screens")+
  ylab("Inspection behind screen (mean)")+
  theme_classic()

p_inspection_complete
```


```{r}
ggsave(p_inspection_complete, filename = "graphics/inspection_opaque_with_zero.png", width=6, height=5, scale=0.7)
```


```{r}
p_inspection<-ggplot(data=inspection_agg2, aes(x=looking_condition, y=mean))+
  geom_bar(stat="identity")+
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=0.5)+
  xlab("Experimenter gaze cue")+
  ylab("Inspection behind opaque screen (mean)")+
  theme_classic()

p_inspection
```


```{r}
#Save 
ggsave(p_inspection, filename = "graphics/inspection_opaque_without_zero.png", width=6, height=5, scale=0.7)
```

### Looking times
```{r}
levels(as.factor(raw.data$Value))
levels(as.factor(raw.data$Behaviour))
levels(as.factor(raw.data$Subject))
duration.data<-raw.data %>%
  droplevels()%>%
  filter(!is.na(trial))%>%
  filter(Value=="Duration looking opaque" | Value=="Duration looking transparent")%>%
  group_by(Subject, trial, Behaviour, Value)%>%
  summarise(sum_duration=sum(duration))%>%
  ungroup()%>%
  droplevels()%>%
  select(-Behaviour)%>%
  complete(Subject, trial, Value, fill=list(sum_duration=0))%>% #fill in 0s
  inner_join(demo.data)%>%
  replace_na(list(sum_duration=0))%>%
  pivot_wider(names_from = Value, values_from=sum_duration)%>%
  rename(duration_transparent="Duration looking transparent", duration_opaque="Duration looking opaque")%>%
  mutate(gaze_congruent_look=as.numeric(ifelse(looking_condition=="transparent", duration_transparent, duration_opaque)), 
         total_looking_time=duration_transparent+duration_opaque,       
         prop_duration_congruent_look=gaze_congruent_look/total_looking_time)

levels(as.factor(duration.data$Subject))

write.csv(duration.data, file = "data/goggles_looking_time_data.csv")
```
### Plot of gaze congruent looking times

```{r}
p_congruent<-ggplot(data=duration.data, aes(x=looking_condition, y=prop_duration_congruent_look))+
  geom_boxplot()+
  xlab("Experimenter gaze cue")+
  ylab("Prop looking time to gaze-congruent target")+
  theme_classic()+
  theme(text = element_text(size = 16)) +
  theme(axis.text = element_text(size = 16)) +
  theme(plot.margin = unit(c(1, 0.1, 0.4, 0.1),
                                "inches"))

p_congruent
```


```{r}
ggsave(p_congruent, filename = "graphics/prop_looking_time_gaze_congruent_target.png", width=4, height=5)
```


```{r}
#plotting absolute looking times to the gaze-congruent target
p_congruent<-ggplot(data=duration.data, aes(x=looking_condition, y=gaze_congruent_look))+
  geom_boxplot()+
  xlab("Experimenter gaze cue")+
  ylab("Absolute looking time to gaze-congruent target")+
  theme_classic()+
  theme(plot.margin = unit(c(0.8, 0.1, 0.2, 0.1),
                                "inches"))+
  theme(axis.title = element_text(size = 16)) +
  theme(axis.text = element_text(size = 14)) 
 
p_congruent

ggsave(p_congruent, filename = "graphics/absolute_looking_time_gaze_congruent_target.png", width=4, height=5)
```
### Looking times to opaque and clear tunnels
```{r}

duration.data2<-raw.data %>%
  droplevels()%>%
  filter(!is.na(trial))%>%
  filter(Value=="Duration looking opaque" | Value=="Duration looking transparent")%>%
  group_by(Subject, trial, Behaviour, Value)%>%
  summarise(sum_duration=sum(duration))%>%
  ungroup()%>%
  droplevels()%>%
  select(-Behaviour)%>%
  complete(Subject, trial, Value, fill=list(sum_duration=0))%>% #fill in 0s
  inner_join(demo.data)%>%
  replace_na(list(sum_duration=0))

p_duration<-ggplot(data=duration.data2, aes(x=Value, y=sum_duration))+
  geom_boxplot()+
  xlab("Duration looking")+
  ylab("Sum duration looking")+
  theme_classic()
    
  p_duration
  
  ggsave(p_duration, filename = "graphics/sum_duration_look.png", width=6, height=5, scale=0.7)


# add multiple plots 
library(cowplot)

pd<-plot_grid(p_duration, p_congruent, labels=c("A", "B"), ncol=2)

ggsave(pd, filename = "graphics/pd.png", width = 10, height=5, scale=0.7)

```
#PLOT OF FIRST LOOK 
```{r}
agg.first.look<-first_look_data%>%
  group_by(looking_condition)%>%
  summarise(mean_first_transparent_look=mean(first_look_transparent), mean_first_look_congr=mean(first_look_cong), se_cong=sd(first_look_cong)/sqrt(length(first_look_cong)) )
```
```{r}
p_fl<-ggplot(data=agg.first.look, aes(x=looking_condition, y=mean_first_look_congr))+
  geom_bar(stat="identity")+
  geom_errorbar(aes(ymin=mean_first_look_congr-se_cong, ymax=mean_first_look_congr+se_cong), width=0.5)+
  xlab("Experimenter gaze cue")+
   ylab("Gaze congruent first look (mean)")+
  theme_classic()

```
## combine multiple plots into one
```{r}
library(cowplot)

combine<-plot_grid(p_choice, p_fl, labels=c("A", "B"), ncol=2)

ggsave(combine, filename = "graphics/combine.png", width = 10, height=5, scale=0.7)
```

## Analysis of proportion looking time
scale covariates
```{r}
# Analysis of looking times
duration.data$z.trial<-scale(duration.data$trial)
duration.data$z.age<-scale(duration.data$age)
```


```{r}
xx.fe.re=fe.re.tab(fe.model="prop_duration_congruent_look~looking_condition+ transparent_screen+trial+age+sex",
re="(1|Subject)", data=duration.data)

duration.data2<-xx.fe.re$data

duration.data2$z.trial<-(duration.data2$trial-mean(duration.data2$trial))/sd(duration.data2$trial)
duration.data2$z.age<-(duration.data2$age-mean(duration.data2$age))/sd(duration.data2$age)
duration.data2$looking_condition.transparent.c<-duration.data2$looking_condition.transparent-mean(duration.data2$looking_condition.transparent)
duration.data2$transparent_screen.yellow.c<-duration.data2$transparent_screen.yellow-mean(duration.data2$transparent_screen.yellow)
```



Remove 1 and 0 from the distribution of the response variable

```{r}
duration.data2$resp <- (duration.data2$prop_duration_congruent_look*(length(duration.data2$prop_duration_congruent_look) - 1) + 0.5)/length(duration.data2$prop_duration_congruent_look) 

#duration.data2<-duration.data2%>%drop_na(resp)

hist(duration.data2$prop_duration_congruent_look)
hist(duration.data2$resp)

min(duration.data2$resp)
max(duration.data2$resp)
```


```{r}
library(glmmTMB)
mm1_duration=glmmTMB(resp~looking_condition+ transparent_screen+
            z.trial+z.age+sex+ (1|Subject) + 
            (0+z.trial|Subject)+(0+looking_condition.transparent.c|Subject), family=beta_family, data=duration.data2,
      control=glmmTMBControl(optCtrl=list(iter.max=100000000, eval.max=100000000)))

summary(mm1_duration)
```

```{r}
overdisp.test(mm1_duration)
```


```{r}
mm1_duration.drop1<-as.data.frame(drop1(mm1_duration, test="Chisq", control=contr))
###tail.mm3.drop1<-tail.mm3.drop1%>%filter(!is.na(Df))%>%add_row(Df = rep(NA,3),  .before = 1)
mm1_duration.drop1
```

stability
```{r}
duration.beta.stab=glmmTMB.stab(model.res=mm1_duration, para=F, data=duration.data2)

duration.beta.stab$summary

m.stab.plot(round(duration.beta.stab$summary[1:6, -1], 2))
#is.re=grepl(x=rownames(mm1.beta.stab$summary), pattern="@")
#m.stab.plot(mm1.beta.stab$summary[!is.re, -1])
```

confidence intervals 


```{r}
duration.data2<-as.data.frame(duration.data2)
source("./functions/boot_glmm.r")
boot.res.duration=boot.glmmtmb(mm1_duration,data=duration.data2, nboots=1000, para=T, level=0.95, n.cores = "all-1")

boot.res.duration$ci.estimates$fe[1:6,]
```
vif 
```{r}
library(car)
xx=lm(resp~looking_condition+transparent_screen+z.trial+z.age+sex, data=duration.data2)
vif(xx)
```
### output table

```{r}
model_table_1<- bind_cols(as.data.frame(summary(mm1_duration)$coefficients$cond),
                             mm1_duration.drop1,
                             boot.res.duration$ci.estimates$fe[1:6,],
                             duration.beta.stab$summary[1:6,-1]) %>% 
  select(Estimate, SE = `Std. Error`, Chi2 = `LRT`, df = `Df`, p = `Pr(>Chi)`,LowerCI = `X2.5.`, UpperCI = `X97.5.`, min, max) %>%
  mutate(across(.cols = c(p), ~ format(round(.x, 3), nsmall=3))) %>%
  mutate(across(.cols = c(Estimate:Chi2), ~ format(round(.x, 2), nsmall=2))) %>%
  mutate(across(.cols = c(LowerCI:max), ~ format(round(.x, 2), nsmall=2))) 
  #mutate(across(Chi2:p, ~replace_na(.x, "")))%>%
  #mutate(p=replace(p, p==0, "<.001"))

model_table_1

write.csv(model_table_1, file = "saves/mm1_duration_output_table.csv")
```


## Analysis of first look
scale covariates
```{r}
# Analysis of first look
first_look_data$z.trial<-scale(first_look_data$trial)
first_look_data$z.age<-scale(first_look_data$age)

#manually dummy code and center looking_condition for random slope component 
first_look_data$looking_condition.c<-as.factor(first_look_data$looking_condition)
first_look_data$looking_condition.c<-as.vector(scale(
  as.numeric(
    first_look_data$looking_condition.c == levels(as.factor(
      first_look_data$looking_condition.c
    ))[2]
  ),
  center = TRUE,
  scale = FALSE
))
```

```{r}
library(lme4)
#
mm1_fl<-glmer(first_look_cong ~ looking_condition+ transparent_screen+
            z.trial+z.age+sex+
            (1+z.trial+looking_condition.c|Subject), family=binomial, data=first_look_data, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

```

```{R echo=FALSE, error=FALSE, warning=FALSE}
library(car)
col.full.fl <- lm(first_look_cong ~ looking_condition+ transparent_screen+ z.trial+z.age+sex, data = first_look_data)
vif(col.full.fl)
#no problem
```
Check model stability
```{r eval=FALSE, echo=FALSE}
m.stab.fl <- glmm.model.stab(model.res = mm1_fl)
m.stab.fl$detailed$warnings
as.data.frame(round(m.stab.fl$summary[1:6, -1], 2))

m.stab.plot(round(m.stab.fl$summary[, -1], 2))
```

####Model output
  + Coefficients
```{r}
round(summary(mm1_fl)$coefficients, 2)
```
Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (R function drop1 with argument 'test' set to "Chisq"). 

```{r}
drop1.mm1_fl=drop1(mm1_fl, test="Chisq")
round(drop1.mm1_fl,3)
```

confidence intervals

```{r}
boot.res.mm1_fl=boot.glmm.pred(model.res=mm1_fl, excl.warnings=T,	nboots=1000, para=F)
ci.res.mm1_fl<-round(boot.res.mm1_fl$ci.estimates, 2)
ci.res.mm1_fl
```

```{r}
save.image(file="goggles_workspace.RData")
```


### output table - first look

```{r}
model_table_fl<- bind_cols(as.data.frame(summary(mm1_fl)$coefficients),
                             drop1.mm1_fl,
                             boot.res.mm1_fl$ci.estimates[1:6,],
                             m.stab.fl$summary[1:6, -1]) %>% 
  select(Estimate, SE = `Std. Error`, Chi2 = LRT, df = npar, p = `Pr(Chi)`, LowerCI = X2.5., UpperCI = X97.5., min, max) %>%  
  mutate(across(.cols = c(p), ~ format(round(.x, 3), nsmall=3))) %>% 
  mutate(across(.cols = c(Estimate:Chi2), ~ format(round(.x, 2), nsmall=2))) %>% 
  mutate(across(.cols = c(LowerCI:max), ~ format(round(.x, 2), nsmall=2))) 
  # mutate(across(Chi2:p, ~replace_na(.x, "")))%>%
  # mutate(p=replace(p, p==0, "<.001"))
model_table_fl
write.csv(model_table_fl, file = "saves/mm1_first_look_output_table.csv")
```

#Analysis of first choice 
scale covariates
```{r}
first_choice_data$z.trial<-scale(first_choice_data$trial)
first_choice_data$z.age<-scale(first_choice_data$age)

#manually dummy code and centre looking condition for random slope component
first_choice_data$looking_condition.c<-as.factor(first_choice_data$looking_condition)
first_choice_data$looking_condition.c<-as.vector(scale(
  as.numeric(
    first_choice_data$looking_condition.c == levels(as.factor(
      first_choice_data$looking_condition.c
    ))[2]
  ),
  center = TRUE,
  scale = FALSE
))
```

```{r}
library(lme4)

mm1_fc<-glmer(first_choice_cong ~ looking_condition+ transparent_screen+
            z.trial+z.age+sex+
            (1+z.trial+looking_condition.c|Subject), family=binomial, data=first_choice_data, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

```
```{R echo=FALSE, error=FALSE, warning=FALSE}
library(car)
col.full.fc <- lm(first_choice_cong ~ looking_condition+ transparent_screen+ z.trial+z.age+sex, data = first_choice_data)
vif(col.full.fc)
#no problem
```
Model stability
```{r eval=FALSE, echo=FALSE}
m.stab.fc <- glmm.model.stab(model.res = mm1_fc)
#Warning: for 8 subset(s) the full model could not be fitted because of fixed effects factor levels dropped from the data

m.stab.fc$detailed$warnings
#most of the models failed to converge 

as.data.frame(round(m.stab.fc$summary[1:6, -1], 2))

m.stab.plot(round(m.stab.fc$summary[, -1], 3))

```

####Model output
  + Coefficients
```{r}
round(summary(mm1_fc)$coefficients, 3)
```
  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 

```{r}
drop1.mm1_fc=drop1(mm1_fc, test="Chisq")
round(drop1.mm1_fc,3)
```

 + confidence intervals

```{r}
boot.res.mm1_fc=boot.glmm.pred(model.res=mm1_fc, excl.warnings=F,	nboots=1000, para=T, n.cores="all-1", resol=1000, level=0.95)

ci.res.mm1_fc<-round(boot.res.mm1_fc$ci.estimates, 2)
ci.res.mm1_fc
```

```{r}
save.image(file="goggles_workspace.RData")
```


### output table - first choice

```{r}
model_table_fc<- bind_cols(as.data.frame(summary(mm1_fc)$coefficients),
                             drop1.mm1_fc,
                             m.stab.fc$summary[1:6, -1],
                             boot.res.mm1_fc$ci.estimates)%>%
                          
  select(Estimate, SE = `Std. Error`, Chi2 = LRT, df = npar, p = `Pr(Chi)`, LowerCI = X2.5., UpperCI = X97.5., min, max) %>%
  mutate(across(.cols = c(p), ~ format(round(.x, 3), nsmall=3))) %>% 
  mutate(across(.cols = c(Estimate:Chi2), ~ format(round(.x, 2), nsmall=2))) %>% 
  mutate(across(.cols = c(LowerCI:max), ~ format(round(.x, 2), nsmall=2))) 
# mutate(across(Chi2:p, ~replace_na(.x, "")))%>%
# mutate(p=replace(p, p==0, "<0.001"))

write.csv(model_table_fc, file = "saves/mm1_first_choice_output_table.csv")
```



## Analysis of inspection behind barrier without zeros 
scale covariates
```{r}
inspection_data$z.trial<-scale(inspection_data$trial)
inspection_data$z.age<-scale(inspection_data$age)

#dummy code and centre condition
inspection_data$looking_condition.c <-
  as.vector(scale(
    as.numeric(
      inspection_data$looking_condition==levels(as.factor(
        inspection_data$looking_condition))[2]),
      scale = FALSE,
      center = TRUE
   
  ))
```

```{r}
library(lme4)
#
mm1_inspection<-glmer(inspection_opaque ~ looking_condition+ transparent_screen+
            z.trial+z.age+sex+
            (1+z.trial+looking_condition.c|Subject), family=binomial, data=inspection_data, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

```

```{R echo=FALSE, error=FALSE, warning=FALSE}
library(car)
col.insp <- lm(inspection_opaque ~ looking_condition+ transparent_screen+ z.trial+ z.age+ sex, data = inspection_data)
vif(col.insp)
#no problem
```
Check model stability
```{r eval=FALSE, echo=FALSE}
m.stab.insp <- glmm.model.stab(model.res = mm1_inspection)
m.stab.insp$detailed$warnings
as.data.frame(round(m.stab.insp$summary[1:6, -1], 2))

m.stab.plot(round(m.stab.insp$summary[, -1], 3))

```

####Model output
  + Coefficients
```{r}
round(summary(mm1_inspection)$coefficients, 2)
```
  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 

```{r}
drop1.insp=drop1(mm1_inspection, test="Chisq")
round(drop1.insp,3)
```

 + confidence intervals

```{r}
boot.res=boot.glmm.pred(model.res=mm1_inspection, excl.warnings=F,	nboots=1000, para=T, n.cores="all-1", resol=1000, level=0.95)
res.insp<-round(boot.res$ci.estimates, 2)
res.insp
```

```{r}
save.image(file="goggles_workspace.RData")
```

### output table - inspections behind opaque tunnel without zeros

```{r}
model_table_insp<- bind_cols(as.data.frame(summary(mm1_inspection)$coefficients),
                             drop1.insp,
                             m.stab.insp$summary[1:6, -1],
                             res.insp)%>%
  select(Estimate, SE = `Std. Error`, Chi2 = LRT, df = npar, p = `Pr(Chi)`, LowerCI = X2.5., UpperCI = X97.5., min, max) %>% 
  mutate(across(.cols = c(p), ~ format(round(.x, 3), nsmall=3))) %>% 
  mutate(across(.cols = c(Estimate:df), ~ format(round(.x, 2), nsmall=2))) %>%
  mutate(across(.cols = c(LowerCI:max), ~ format(round(.x, 2), nsmall=2))) 
  # mutate(across(Chi2:p, ~replace_na(.x, "")))%>%
  # mutate(p=replace(p, p==0, "<0.001"))

write.csv(model_table_insp, file = "saves/mm1_inspection_without_zero_output_table.csv")
```




## Analysis of inspection behind barrier with zeros 
scale covariates
```{r}
inspection_data_complete$z.trial<-scale(inspection_data_complete$trial)
inspection_data_complete$z.age<-scale(inspection_data_complete$age)
```

```{r}
library(lme4)
#
mm1_inspection<-glmer(inspection_opaque ~ looking_condition+ transparent_screen+
            z.trial+z.age+sex+
            (1+z.trial+looking_condition|Subject), family=binomial, data=inspection_data_complete, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

```

```{R echo=FALSE, error=FALSE, warning=FALSE}
library(car)
col.insp.1 <- lm(inspection_opaque ~ looking_condition+ transparent_screen+ z.trial+ z.age+ sex, data = inspection_data)
vif(col.insp.1)
#no problem
```
Check model stability
```{r eval=FALSE, echo=FALSE}
m.stab.insp <- glmm.model.stab(model.res = mm1_inspection)
m.stab.insp$detailed$warnings
xx <- as.data.frame(round(m.stab.insp$summary[, -1], 3))
xx
m.stab.plot(round(m.stab.insp$summary[, -1], 3))

```

####Model output
  + Coefficients
```{r}
round(summary(mm1_inspection)$coefficients, 3)
```
  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 

```{r}
drop1.insp=drop1(mm1_inspection, test="Chisq")
round(drop1.insp,3)
```

 + confidence intervals

```{r}
boot.res=boot.glmm.pred(model.res=mm1_inspection, excl.warnings=T,	nboots=1000, para=F)
res.insp<-round(boot.res$ci.estimates, 3)
res.insp
```


```{r}
save.image(file="goggles_workspace.RData")
```



### output table

```{r}
#model_tail_cis=grepl(x=rownames(mm3_tail.ci$ci.estimates$fe), pattern="@cond")

model_table_insp<- bind_cols(as.data.frame(summary(mm1_inspection)$coefficients),
                             drop1.insp)%>%
                            # mm3_tail.ci$ci.estimates$fe[1:7,]) %>%
  select(Estimate, SE = `Std. Error`, Chi2 = LRT, df = npar, p = `Pr(Chi)`) %>% #LowerCI = X2.5., UpperCI = X97.5., 
  mutate(across(.cols = c(p), ~ format(round(.x, 3), nsmall=3))) %>% 
  mutate(across(.cols = c(Estimate:Chi2), ~ format(round(.x, 2), nsmall=2))) %>% 
  mutate(across(Chi2:p, ~replace_na(.x, "")))%>%
mutate(p=replace(p, p==0, "<0.001"))

write.csv(model_table_insp, file = "saves/mm1_inspection_with_zero_output_table.csv")
```




## Analysis of absolute looking time to transparent barrier
```{r}
transparent.duration.data<-raw.data %>%
  droplevels()%>%
  filter(!is.na(trial))%>%
  filter(Value=="Duration looking opaque" | Value=="Duration looking transparent")%>%
  group_by(Subject, trial, Behaviour, Value)%>%
  summarise(sum_duration=sum(duration))%>%
  ungroup()%>%
  droplevels()%>%
  select(-Behaviour)%>%
  complete(Subject, trial, Value, fill=list(sum_duration=0))%>% #fill in 0s
  inner_join(demo.data)%>%
  replace_na(list(sum_duration=0))%>%
  filter(Value=="Duration looking transparent")
```

### plot of absolute looking time to transparent screen
```{r}
hist(transparent.duration.data$sum_duration)
hist(sqrt(transparent.duration.data$sum_duration))
ggplot(data=transparent.duration.data, aes(x=looking_condition, y=sum_duration))+
  geom_boxplot()

p_trans_dur<-ggplot(data=transparent.duration.data, aes(x=looking_condition, y=sum_duration))+
  geom_boxplot()+
  xlab("Experimenter gaze cue")+
  ylab("Duration looking transparent")+
  theme_classic()

p_trans_dur
```


```{r}
ggsave(p_trans_dur, filename = "graphics/duration_transparent.png", width=6, height=5, scale=0.7)
```


scale covariates
```{r}
transparent.duration.data$z.trial<-scale(transparent.duration.data$trial)
transparent.duration.data$z.age<-scale(transparent.duration.data$age)

#manual dummy coding and centering the factors for random slope component
transparent.duration.data$looking_condition_dummy.c <- as.factor(transparent.duration.data$looking_condition)

levels(transparent.duration.data$looking_condition_dummy.c)

transparent.duration.data$looking_condition_dummy.c = as.vector(scale(
  as.numeric(
    transparent.duration.data$looking_condition_dummy.c == levels(as.factor(
      transparent.duration.data$looking_condition
    ))[2]
  ),
  center = TRUE,
  scale = FALSE
))

```

### fitting LMM 
```{r}
library(lme4)

mm1_transparent<-lmer(sqrt(sum_duration) ~ looking_condition+ transparent_screen+
            z.trial+z.age+sex+
            (1+z.trial+looking_condition_dummy.c|Subject), REML=FALSE, data=transparent.duration.data)
```

Assumptions and stability
```{r}
diagnostics.plot(mm1_transparent)
ranef.diagn.plot(mm1_transparent)

full.stab.transp=glmm.model.stab(model.res=mm1_transparent, contr=NULL, para=F, data=transparent.duration.data)
m.stab.plot(full.stab.transp$summary[, -1])
round(full.stab.transp$summary[1:6,-1],2)
```

Model output
```{r}
#coefficients
summary(mm1_transparent)$coefficients

library(lmerTest)
mm1_transparent.reml<-lmerTest::lmer(sqrt(sum_duration) ~ looking_condition+ transparent_screen+
            z.trial+z.age+sex+
            (1+z.trial+looking_condition_dummy.c|Subject), REML=T, data=transparent.duration.data)

#p-values
round(summary(mm1_transparent.reml)$coefficients,3)
```


 + confidence intervals

```{r}
boot.res.trans=boot.glmm.pred(model.res=mm1_transparent, excl.warnings=F,	nboots=1000, para=T, n.cores="all-1", resol=1000, level=0.95)

res.trans<-round(boot.res.trans$ci.estimates, 3)
res.trans
```

###Output table - absolute looking time to transparent
```{r}

model_table_transp<- bind_cols(as.data.frame(summary(mm1_transparent)$coefficients),
                             summary(mm1_transparent.reml)$coefficients[,3:5],
                             full.stab.transp$summary[1:6, -1],
                             boot.res.trans$ci.estimates)%>%
  select(Estimate, SE = `Std. Error`, t =`t value...3`, df, p=`Pr(>|t|)`, LowerCI = X2.5., UpperCI = X97.5., min, max) %>%  
  mutate(across(.cols = c(p), ~ format(round(.x, 3), nsmall=3))) %>% 
  mutate(across(.cols = c(Estimate:t), ~ format(round(.x, 2), nsmall=2))) %>% 
  mutate(across(.cols = c(LowerCI:max), ~ format(round(.x, 2), nsmall=2))) 
# mutate(across(Chi2:p, ~replace_na(.x, "")))%>%
# mutate(p=replace(p, p==0, "<0.001"))

write.csv(model_table_transp, file = "saves/mm1_abs_lt_transp_output_table.csv")
```

## Looking time to opaque barrier

```{r}

opaque.duration.data<-raw.data %>%
  droplevels()%>%
  filter(!is.na(trial))%>%
  filter(Value=="Duration looking opaque" | Value=="Duration looking transparent")%>%
  group_by(Subject, trial, Behaviour, Value)%>%
  summarise(sum_duration=sum(duration))%>%
  ungroup()%>%
  droplevels()%>%
  select(-Behaviour)%>%
  complete(Subject, trial, Value, fill=list(sum_duration=0))%>% #fill in 0s
  inner_join(demo.data)%>%
  replace_na(list(sum_duration=0))%>%
  filter(Value=="Duration looking opaque")


p_opaque_dur<-ggplot(data=opaque.duration.data, aes(x=looking_condition, y=sum_duration))+
  geom_boxplot()+
  xlab("Experimenter gaze cue")+
  ylab("Absolute looking time to opaque")+
  theme_classic()

p_opaque_dur

ggsave(p_opaque_dur, filename = "graphics/abs_lt_opaque.png", width=6, height=5, scale=0.7)

hist(opaque.duration.data$sum_duration) #also skewed
hist(sqrt(opaque.duration.data$sum_duration)) #better, we use this as response
```
scale covariates
```{r}
opaque.duration.data$z.trial<-scale(opaque.duration.data$trial)
opaque.duration.data$z.age<-scale(opaque.duration.data$age)

#manual dummy coding and centering of factor
opaque.duration.data$looking_condition_dummy.c=as.vector(scale(as.numeric(opaque.duration.data$looking_condition==levels(as.factor(opaque.duration.data$looking_condition))[2]),
                                                               center=TRUE,
                                                               scale=FALSE))
```

### fitting LMM 
```{r}
library(lme4)

mm1_opaque<-lmer(sqrt(sum_duration) ~ looking_condition+ transparent_screen+
            z.trial+z.age+sex+
            (1+z.trial+looking_condition_dummy.c|Subject), REML=FALSE, data=opaque.duration.data)
```

Assumptions and stability
```{r}
diagnostics.plot(mm1_opaque)
ranef.diagn.plot(mm1_opaque)
full.stab.opaque=glmm.model.stab(model.res=mm1_opaque, contr=NULL, para=F, data=opaque.duration.data)

m.stab.plot(full.stab.opaque$summary[, -1])
full.stab.opaque$summary[1:6, -1]
```

Model output
```{r}
summary(mm1_opaque)$coefficients

library(lmerTest)
mm1_opaque.reml<-lmerTest::lmer(sqrt(sum_duration) ~ looking_condition+ transparent_screen+
            z.trial+z.age+sex+
            (1+z.trial+looking_condition_dummy.c|Subject), REML=T, data=opaque.duration.data)

#p-values
round(summary(mm1_opaque.reml)$coefficients,3)

```
 + confidence intervals

```{r}
boot.res.opa=boot.glmm.pred(model.res=mm1_opaque, excl.warnings=F,	nboots=1000, para=T, n.cores="all-1", resol=1000, level=0.95)
res.opa<-round(boot.res.opa$ci.estimates, 2)
res.opa
```
### Output table - absolute looking time to opaque

```{r}


model_table_opaque<- bind_cols(as.data.frame(summary(mm1_opaque)$coefficients),
                            summary(mm1_opaque.reml)$coefficients[,3:5],
                            full.stab.opaque$summary[1:6, -1],
                            res.opa)%>%
  select(Estimate, SE = `Std. Error`, t = `t value...3`, df , p = `Pr(>|t|)`, LowerCI = X2.5., UpperCI = X97.5., min, max)%>% 
  mutate(across(.cols = c(p), ~ format(round(.x, 3), nsmall=3))) %>% 
  mutate(across(.cols = c(Estimate:df), ~ format(round(.x, 2), nsmall=2))) %>% 
  mutate(across(.cols = c(LowerCI:max), ~ format(round(.x, 2), nsmall=2)))  
  # mutate(across(Chi2:p, ~replace_na(.x, "")))%>%
  # mutate(p=replace(p, p==0, "<0.001"))

write.csv(model_table_opaque, file = "saves/mm1_abs_lt_opaque_output_table.csv")
```
### combine multiple plots into one 
```{r}

library(cowplot)

fl_dur<-plot_grid(p_trans_dur, p_opaque_dur, labels=c("A", "B"), ncol=2)

ggsave(fl_dur, filename = "graphics/fl_dur.png", width = 10, height=5, scale=0.7)
```
#Analysis of whether the probability that dogs looked to the transparent screen at least once during a trial was influenced by looking condition

```{r}
duration.data3<-duration.data %>% 
  mutate(looked_transp=ifelse(duration_transparent>0,1,0)) # did the dog look to the transparent screen at least once during a trial?
```

```{r}
#scale covariates
duration.data3$z.trial<-scale(duration.data3$trial)
duration.data3$z.age<-scale(duration.data3$age)
#dummy code and centre condition for random slope component
duration.data3$looking_condition.c <-
  as.vector(scale(
    as.numeric(
      duration.data3$looking_condition==levels(as.factor(
        duration.data3$looking_condition))[2]),
      scale = FALSE,
      center = TRUE
   
  ))

#fitting binomial model
library(lme4)
at_least1_look_transp<-glmer(looked_transp ~ looking_condition+ transparent_screen+
            z.trial+z.age+sex+
            (1+z.trial+looking_condition.c|Subject), family=binomial, data=duration.data3, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
```

```{R echo=FALSE, error=FALSE, warning=FALSE}
library(car)
col.at_least1_look_transp <- lm(looked_transp ~ looking_condition+ transparent_screen+ z.trial+z.age+sex, data = duration.data3)
vif(col.at_least1_look_transp)
#no problem
```
Check model stability
```{r eval=FALSE, echo=FALSE}
stab.at_least1_look_transp <- glmm.model.stab(model.res = at_least1_look_transp)
stab.at_least1_look_transp$detailed$warnings
as.data.frame(round(stab.at_least1_look_transp$summary[1:6, -1], 2))

m.stab.plot(round(stab.at_least1_look_transp$summary[1:6, -1], 2))

#the estimates vary excessively depending on which subject is excluded. 
```

####Model output
  + Coefficients
```{r}
round(summary(at_least1_look_transp)$coefficients, 2)

#There are issues with this model: complete separation and excessive instability. Hence, we fit it again, removing the correlations between random intercept and slopes below. 
```
Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (R function drop1 with argument 'test' set to "Chisq"). 

```{r}
drop1.at_least1_look_transp=drop1(at_least1_look_transp, test="Chisq")
round(drop1.at_least1_look_transp,2)
```

confidence intervals

```{r}
boot.res.at_least1_look_transp=boot.glmm.pred(model.res=at_least1_look_transp, excl.warnings=F,	nboots=1000, para=T, n.cores="all-1", resol=1000, level=0.95)
ci.res.at_least1_look_transp<-round(boot.res.at_least1_look_transp$ci.estimates, 2)
ci.res.at_least1_look_transp
```

```{r}
save.image(file="goggles_workspace.RData")
```


### output table - at least 1 look to transparent screen during a trial

```{r}
model_table_at_least1_look_transp<- bind_cols(as.data.frame(summary(at_least1_look_transp)$coefficients),
                             drop1.at_least1_look_transp,
                             ci.res.at_least1_look_transp,
                             stab.at_least1_look_transp$summary[1:6, -1]) %>% 
  select(Estimate, SE = `Std. Error`, Chi2 = LRT, df = npar, p = `Pr(Chi)`, LowerCI = X2.5., UpperCI = X97.5., min, max) %>%  
  mutate(across(.cols = c(p), ~ format(round(.x, 3), nsmall=3))) %>% 
  mutate(across(.cols = c(Estimate:Chi2), ~ format(round(.x, 2), nsmall=2))) %>% 
  mutate(across(.cols = c(LowerCI:max), ~ format(round(.x, 2), nsmall=2))) 
  # mutate(across(Chi2:p, ~replace_na(.x, "")))%>%
  # mutate(p=replace(p, p==0, "<.001"))
model_table_at_least1_look_transp
write.csv(model_table_at_least1_look_transp, file = "saves/mm1_at_least1_look_transp_output_table.csv")
```

### Model without correlation between random intercept and slopes
```{r}
#fitting binomial model
library(lme4)
at_least1_look_transp.woc<-glmer(looked_transp ~ looking_condition+ transparent_screen+
            z.trial+z.age+sex+
            (1+z.trial+looking_condition.c||Subject), family=binomial, data=duration.data3, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
```
```{r}
#evaluate stability
stab.at_least1_look_transp.woc <- glmm.model.stab(model.res = at_least1_look_transp.woc)
stab.at_least1_look_transp.woc$detailed$warnings #most models failed to converge
as.data.frame(round(stab.at_least1_look_transp.woc$summary[1:6, -1], 2)) #but the model is more stable than the previous one

m.stab.plot(round(stab.at_least1_look_transp.woc$summary[1:6, -1], 2))

```

### model output
```{r}
round(summary(at_least1_look_transp.woc)$coefficients, 2)
```
Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (R function drop1 with argument 'test' set to "Chisq"). 

```{r}
drop1.at_least1_look_transp.woc=drop1(at_least1_look_transp.woc, test="Chisq")
round(drop1.at_least1_look_transp.woc,3)
```

confidence intervals

```{r}
boot.res.at_least1_look_transp.woc=boot.glmm.pred(model.res=at_least1_look_transp.woc, excl.warnings=F,	nboots=1000, para=T, n.cores="all-1", resol=1000, level=0.95)
ci.res.at_least1_look_transp.woc<-round(boot.res.at_least1_look_transp.woc$ci.estimates, 2)
ci.res.at_least1_look_transp.woc
```
### output table - at least 1 look to transparent screen during a trial without correlations

```{r}
model_table_at_least1_look_transp.woc<- bind_cols(as.data.frame(summary(at_least1_look_transp.woc)$coefficients),
                             drop1.at_least1_look_transp.woc,
                             ci.res.at_least1_look_transp.woc,
                             stab.at_least1_look_transp.woc$summary[1:6, -1]) %>% 
  select(Estimate, SE = `Std. Error`, Chi2 = LRT, df = npar, p = `Pr(Chi)`, LowerCI = X2.5., UpperCI = X97.5., min, max) %>%  
  mutate(across(.cols = c(p), ~ format(round(.x, 3), nsmall=3))) %>% 
  mutate(across(.cols = c(Estimate:Chi2), ~ format(round(.x, 2), nsmall=2))) %>% 
  mutate(across(.cols = c(LowerCI:max), ~ format(round(.x, 2), nsmall=2))) 
  # mutate(across(Chi2:p, ~replace_na(.x, "")))%>%
  # mutate(p=replace(p, p==0, "<.001"))
model_table_at_least1_look_transp.woc
write.csv(model_table_at_least1_look_transp.woc, file = "saves/mm1_at_least1_look_transp_woc_output_table.csv")
```



# First look to transparent barrier

```{r}
first_look_trans_data<-raw.data%>%
  filter(Behaviour=="First look")%>%
  filter(!is.na(trial))%>%
  group_by(Subject, trial)%>%
  summarise(first_look_transparent=sum(Value=="First look transparent"))%>%
  ungroup()%>%
  full_join(demo.data)%>%
  complete(Subject, trial,  fill=list(first_look_transparent=0))#fill in 0s
```

## Analysis of first look transparent
scale covariates
```{r}
# Analysis of first look
first_look_trans_data$z.trial<-scale(first_look_trans_data$trial)
first_look_trans_data$z.age<-scale(first_look_trans_data$age)
```

```{r}
library(lme4)

mm1_flt<-glmer(first_look_transparent ~ looking_condition+ transparent_screen+
            z.trial+z.age+sex+
            (1+z.trial+looking_condition|Subject), family=binomial, data=first_look_trans_data, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

```
```{R echo=FALSE, error=FALSE, warning=FALSE}
library(car)
col.full.flt <- lm(first_look_transparent ~ looking_condition+ transparent_screen+ z.trial+z.age+sex, data = first_look_trans_data)
vif(col.full.flt)
#no problem
```
Check model stability
```{r eval=FALSE, echo=FALSE}
m.stab.flt <- glmm.model.stab(model.res = mm1_flt)
m.stab.flt$detailed$warnings
xx <- as.data.frame(round(m.stab.flt$summary[, -1], 3))
xx
m.stab.plot(round(m.stab.flt$summary[, -1], 3))

```

####Model output
  + Coefficients
```{r}
round(summary(mm1_flt)$coefficients, 3)
```
  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 

```{r}
drop1.flt=drop1(mm1_flt, test="Chisq")
round(drop1.flt,3)
```

 + confidence intervals

```{r}
boot.res.flt=boot.glmm.pred(model.res=mm1_flt, excl.warnings=T,	nboots=1000, para=F)
res.flt<-round(boot.res.flt$ci.estimates, 3)
res.flt
```

```{r}
save.image(file="goggles_workspace.RData")
```



### output table

```{r}
#model_tail_cis=grepl(x=rownames(mm3_tail.ci$ci.estimates$fe), pattern="@cond")

model_table_flt<- bind_cols(as.data.frame(summary(mm1_flt)$coefficients),
                             drop1.flt)%>%
                            # mm3_tail.ci$ci.estimates$fe[1:7,]) %>%
  select(Estimate, SE = `Std. Error`, Chi2 = LRT, df = npar, p = `Pr(Chi)`) %>% #LowerCI = X2.5., UpperCI = X97.5., 
  mutate(across(.cols = c(p), ~ format(round(.x, 3), nsmall=3))) %>% 
  mutate(across(.cols = c(Estimate:Chi2), ~ format(round(.x, 2), nsmall=2))) %>% 
  mutate(across(Chi2:p, ~replace_na(.x, "")))%>%
mutate(p=replace(p, p==0, "<0.001"))

write.csv(model_table_flt, file = "saves/mm1_first_look_trans_output_table.csv")
```

### first look transparent: chance level comparison
```{r}
first_look_trans_agg_data<- first_look_trans_data%>%
  group_by(Subject, looking_condition) %>%
  summarise(mean_trans_fl = mean(first_look_transparent)) 

t.test(first_look_trans_agg_data$mean_trans_fl[first_look_trans_agg_data$looking_condition=="transparent"], mu=0.5)

t.test(first_look_trans_agg_data$mean_trans_fl[first_look_trans_agg_data$looking_condition=="opaque"], mu=0.5)


```

## Analysis of first look opaque
```{r}
first_look_opaque_data<-raw.data%>%
  filter(Behaviour=="First look")%>%
  filter(!is.na(trial))%>%
  group_by(Subject, trial)%>%
  summarise(first_look_opaque=sum(Value=="First look opaque"))%>%
  ungroup()%>%
  full_join(demo.data)%>%
  complete(Subject, trial,  fill=list(first_look_opaque=0))#fill in 0s
```

scale covariates
```{r}
# Analysis of first look opaque
first_look_opaque_data$z.trial<-(first_look_opaque_data$trial-mean(first_look_opaque_data$trial))/sd(first_look_opaque_data$trial)
first_look_opaque_data$z.age<-(first_look_opaque_data$age-mean(first_look_opaque_data$age))/sd(first_look_opaque_data$age)
```

```{r}
library(lme4)

mm1_flo<-glmer(first_look_opaque ~ looking_condition+ transparent_screen+
            z.trial+z.age+sex+
            (1+z.trial+looking_condition|Subject), family=binomial, data=first_look_opaque_data, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

```
```{R echo=FALSE, error=FALSE, warning=FALSE}
library(car)
col.full.flo <- lm(first_look_opaque ~ looking_condition+ transparent_screen+ z.trial+z.age+sex, data = first_look_opaque_data)
vif(col.full.flo)
#no problem
```
Check model stability
```{r eval=FALSE, echo=FALSE}
m.stab.flo <- glmm.model.stab(model.res = mm1_flo)
m.stab.flo$detailed$warnings
xx <- as.data.frame(round(m.stab.flo$summary[, -1], 3))
xx
m.stab.plot(round(m.stab.flo$summary[, -1], 3))

```

####Model output
  + Coefficients
```{r}
round(summary(mm1_flo)$coefficients, 3)
```
  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 

```{r}
drop1.flo=drop1(mm1_flo, test="Chisq")
round(drop1.flo,3)
```

 + confidence intervals

```{r}
boot.res.flo=boot.glmm.pred(model.res=mm1_flo, excl.warnings=T,	nboots=1000, para=F)
res.flo<-round(boot.res.flo$ci.estimates, 3)
res.flo
```

```{r}
save.image(file="goggles_workspace.RData")
```



### output table

```{r}
#model_tail_cis=grepl(x=rownames(mm3_tail.ci$ci.estimates$fe), pattern="@cond")

model_table_flo<- bind_cols(as.data.frame(summary(mm1_flo)$coefficients),
                             drop1.flo)%>%
                            # mm3_tail.ci$ci.estimates$fe[1:7,]) %>%
  select(Estimate, SE = `Std. Error`, Chi2 = LRT, df = npar, p = `Pr(Chi)`) %>% #LowerCI = X2.5., UpperCI = X97.5., 
  mutate(across(.cols = c(p), ~ format(round(.x, 3), nsmall=3))) %>% 
  mutate(across(.cols = c(Estimate:Chi2), ~ format(round(.x, 2), nsmall=2))) %>% 
  mutate(across(Chi2:p, ~replace_na(.x, "")))%>%
mutate(p=replace(p, p==0, "<0.001"))

write.csv(model_table_flo, file = "saves/mm1_first_look_opaque_output_table.csv")
```

### first look opaque: chance level comparison
```{r}
first_look_opaque_agg_data<- first_look_opaque_data%>%
  group_by(Subject, looking_condition) %>%
  summarise(mean_opaque_fl = mean(first_look_opaque)) 

t.test(first_look_opaque_agg_data$mean_opaque_fl[first_look_opaque_agg_data$looking_condition=="transparent"], mu=0.5)

t.test(first_look_opaque_agg_data$mean_opaque_fl[first_look_opaque_agg_data$looking_condition=="opaque"], mu=0.5)

#comparing gaze incongruent looks
t.test(first_look_trans_agg_data$mean_trans_fl[first_look_trans_agg_data$looking_condition=="opaque"], first_look_opaque_agg_data$mean_opaque_fl[first_look_opaque_agg_data$looking_condition=="transparent"], paired=TRUE)

t.test(first_look_trans_agg_data$mean_trans_fl[first_look_trans_agg_data$looking_condition=="opaque"], first_look_opaque_agg_data$mean_opaque_fl[first_look_opaque_agg_data$looking_condition=="opaque"], paired=TRUE)

t.test(first_look_trans_agg_data$mean_trans_fl[first_look_trans_agg_data$looking_condition=="transparent"], first_look_opaque_agg_data$mean_opaque_fl[first_look_opaque_agg_data$looking_condition=="transparent"], paired=TRUE)

```
#Analysis of first choice transparent 
```{r}
first_choice_trans_data<-raw.data%>%
  filter(Behaviour=="First target choice")%>%
  filter(!is.na(trial))%>%
  group_by(Subject, trial)%>%
  summarise(first_choice_transparent=sum(Value=="First choice transparent"))%>%
  ungroup()%>%
  full_join(demo.data)%>%
  complete(Subject, trial,  fill=list(first_choice_transparent=0))#fill in 0s
```


scale covariates
```{r}
# Analysis of first choice
first_choice_trans_data$z.trial<-scale(first_choice_trans_data$trial)
first_choice_trans_data$z.age<-scale(first_choice_trans_data$age)
```

```{r}
library(lme4)
max(first_choice_trans_data$first_choice_transparent)
mm1_fct<-glmer(first_choice_transparent ~ looking_condition+ transparent_screen+
            z.trial+z.age+sex+
            (1+z.trial+looking_condition|Subject), family=binomial, data=first_choice_trans_data, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

```





```{R echo=FALSE, error=FALSE, warning=FALSE}
library(car)
col.full.fct <- lm(first_choice_transparent ~ looking_condition+ transparent_screen+ z.trial+z.age+sex, data = first_choice_trans_data)
vif(col.full.fct)
#no problem
```
Model stability
```{r eval=FALSE, echo=FALSE}
m.stab.fct <- glmm.model.stab(model.res = mm1_fct)
m.stab.fct$detailed$warnings
xx <- as.data.frame(round(m.stab.fct$summary[, -1], 3))
xx
m.stab.plot(round(m.stab.fct$summary[, -1], 3))

```

####Model output
  + Coefficients
```{r}
round(summary(mm1_fct)$coefficients, 3)
```
  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 

```{r}
drop1.mm1_fct=drop1(mm1_fct, test="Chisq")
round(drop1.mm1_fct,3)
```

 + confidence intervals

```{r}
boot.res.mm1_fct=boot.glmm.pred(model.res=mm1_fct, excl.warnings=T,	nboots=1000, para=F)
ci.res.mm1_fct<-round(boot.res.mm1_fct$ci.estimates, 3)
ci.res.mm1_fct
```

```{r}
save.image(file="goggles_workspace.RData")
```


### output table

```{r}
model_table_fct<- bind_cols(as.data.frame(summary(mm1_fct)$coefficients),
                             drop1.mm1_fct,
                             m.stab.fct$summary[, -1],
                             boot.res.mm1_fct$ci.estimates)%>%
  select(Estimate, SE = `Std. Error`, Chi2 = LRT, df = npar, p = `Pr(Chi)`, LowerCI = X2.5., UpperCI = X97.5., min, max) %>%
  mutate(across(.cols = c(p), ~ format(round(.x, 3), nsmall=3))) %>% 
  mutate(across(.cols = c(Estimate:Chi2), ~ format(round(.x, 2), nsmall=2))) %>% 
# mutate(across(Chi2:p, ~replace_na(.x, "")))%>%
# mutate(p=replace(p, p==0, "<0.001"))

write.csv(model_table_fc, file = "saves/mm1_first_choice_transparent_output_table.csv")
```

## First trial analysis

### First look congruent
only first trial
```{r}
first_look_data_trial1<-first_look_data%>%
  filter(trial==1)
```


scale covariates
```{r}
# Analysis of first look
first_look_data_trial1$z.age<-scale(first_look_data_trial1$age)
```

```{r}
library(lme4)
mm1_fl_trial1<-glm(first_look_cong ~ looking_condition+ transparent_screen+
            z.age+sex, family=binomial, data=first_look_data_trial1)

```


```{R echo=FALSE, error=FALSE, warning=FALSE}
library(car)
col.mm1_fl_trial1 <- lm(first_look_cong ~ looking_condition+ transparent_screen+ z.age+sex, data = first_look_data_trial1)
vif(col.mm1_fl_trial1)
#no problem
```
Check model stability
```{r eval=FALSE, echo=FALSE}
summary(mm1_fl_trial1)

#dfBeta values
cbind(coef(mm1_fl_trial1),
coef(mm1_fl_trial1)+t(apply(dfbeta(mm1_fl_trial1), 2, range)))

```

####Model output
  + Coefficients
```{r}
round(summary(col.mm1_fl_trial1)$coefficients, 3)
```
  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 

```{r}
drop1.mm1_fl_trial1=drop1(mm1_fl_trial1, test="Chisq")
round(drop1.mm1_fl_trial1,3)
```

 + confidence intervals

```{r}
boot.res.mm1_fl_trial1=boot.glmm.pred(model.res=mm1_fl_trial1, excl.warnings=T,	nboots=1000, para=F)
ci.res.mm1_fl_trial1<-round(boot.res.mm1_fl_trial1$ci.estimates, 3)
ci.res.mm1_fl_trial1
```

```{r}
save.image(file="goggles_workspace.RData")
```


### output table
```{r}
#model_tail_cis=grepl(x=rownames(mm3_tail.ci$ci.estimates$fe), pattern="@cond")

model_table_fl_trial1<- bind_cols(as.data.frame(summary(mm1_fl_trial1)$coefficients),
                             drop1.mm1_fl_trial1)%>%
                            # ci.res.mm1_fl$ci.estimates$fe[1:6,]) %>%
  select(Estimate, SE = `Std. Error`, Chi2 = LRT, df = npar, p = `Pr(Chi)`) %>% #LowerCI = X2.5., UpperCI = X97.5., 
  mutate(across(.cols = c(p), ~ format(round(.x, 3), nsmall=3))) %>% 
  mutate(across(.cols = c(Estimate:Chi2), ~ format(round(.x, 2), nsmall=2))) %>% 
  mutate(across(Chi2:p, ~replace_na(.x, "")))%>%
mutate(p=replace(p, p==0, "<0.001"))

write.csv(model_table_fl_trial1, file = "saves/mm1_first_look_trial1_output_table.csv")
```

# Exploratory analyses excluding dogs that did not pass manipulation check immediately
```{r}
dogs.to.excl<-c("Toulouse", "Samira", "JellyBean", "Joseph", "Elvis3", "Ronja7", "Nemo1", "Jasper", "Jessy9")
```

## Proportion looking time to gaze-congruent screen
scale covariates
```{r}

duration.data.23dogs<- duration.data %>% 
  filter(!Subject %in% dogs.to.excl)

duration.data.23dogs$z.trial<-scale(duration.data.23dogs$trial)
duration.data.23dogs$z.age<-scale(duration.data.23dogs$age)
```


```{r}
xx.fe.re=fe.re.tab(fe.model="prop_duration_congruent_look~looking_condition+ transparent_screen+trial+age+sex",
re="(1|Subject)", data=duration.data.23dogs)

duration.data.23dogs<-xx.fe.re$data

duration.data.23dogs$z.trial<-(duration.data.23dogs$trial-mean(duration.data.23dogs$trial))/sd(duration.data.23dogs$trial)

duration.data.23dogs$z.age<-(duration.data.23dogs$age-mean(duration.data.23dogs$age))/sd(duration.data.23dogs$age)

duration.data.23dogs$looking_condition.transparent.c<-duration.data.23dogs$looking_condition.transparent-mean(duration.data.23dogs$looking_condition.transparent)

duration.data.23dogs$transparent_screen.yellow.c<-duration.data.23dogs$transparent_screen.yellow-mean(duration.data.23dogs$transparent_screen.yellow)
```



Remove 1 and 0 from the distribution of the response variable

```{r}
duration.data.23dogs$resp <- (duration.data.23dogs$prop_duration_congruent_look*(length(duration.data.23dogs$prop_duration_congruent_look) - 1) + 0.5)/length(duration.data.23dogs$prop_duration_congruent_look) 


hist(duration.data.23dogs$prop_duration_congruent_look)
hist(duration.data.23dogs$resp)

min(duration.data.23dogs$resp)
max(duration.data.23dogs$resp)
```


```{r}
library(glmmTMB)
mm2_duration=glmmTMB(resp~looking_condition+ transparent_screen+
            z.trial+z.age+sex+ (1|Subject) + 
            (0+z.trial|Subject)+(0+looking_condition.transparent.c|Subject), family=beta_family, data=duration.data.23dogs,
      control=glmmTMBControl(optCtrl=list(iter.max=100000000, eval.max=100000000)))

summary(mm2_duration)
```

```{r}
overdisp.test(mm2_duration)
```


```{r}
mm2_duration.drop1<-as.data.frame(drop1(mm2_duration, test="Chisq", control=contr))
###tail.mm3.drop1<-tail.mm3.drop1%>%filter(!is.na(Df))%>%add_row(Df = rep(NA,3),  .before = 1)
mm2_duration.drop1
```

stability
```{r}
duration.beta2.stab=glmmTMB.stab(model.res=mm2_duration, para=F, data=duration.data.23dogs)

duration.beta2.stab$summary

m.stab.plot(round(duration.beta2.stab$summary[1:6, -1], 2))
#is.re=grepl(x=rownames(mm1.beta.stab$summary), pattern="@")
#m.stab.plot(mm1.beta.stab$summary[!is.re, -1])
```

confidence intervals 


```{r}
duration.data.23dogs<-as.data.frame(duration.data.23dogs)
source("./functions/boot_glmm.r")
boot.res.duration2=boot.glmmtmb(mm2_duration,data=duration.data.23dogs, nboots=1000, para=T, level=0.95, n.cores = "all-1")

boot.res.duration2$ci.estimates$fe[1:6,]
```
vif 
```{r}
library(car)
xx=lm(resp~looking_condition+transparent_screen+z.trial+z.age+sex, data=duration.data.23dogs)
vif(xx)
```
### output table

```{r}
model_table_prop_lt_23_dogs<- bind_cols(as.data.frame(summary(mm2_duration)$coefficients$cond),
                             mm2_duration.drop1,
                             boot.res.duration2$ci.estimates$fe[1:6,],
                             duration.beta2.stab$summary[1:6,-1]) %>% 
  select(Estimate, SE = `Std. Error`, Chi2 = `LRT`, df = `Df`, p = `Pr(>Chi)`,LowerCI = `X2.5.`, UpperCI = `X97.5.`, min, max) %>%
  mutate(across(.cols = c(p), ~ format(round(.x, 3), nsmall=3))) %>%
  mutate(across(.cols = c(Estimate:Chi2), ~ format(round(.x, 2), nsmall=2))) %>%
  mutate(across(.cols = c(LowerCI:max), ~ format(round(.x, 2), nsmall=2))) 
  #mutate(across(Chi2:p, ~replace_na(.x, "")))%>%
  #mutate(p=replace(p, p==0, "<.001"))

model_table_prop_lt_23_dogs

write.csv(model_table_prop_lt_23_dogs, file = "saves/mm2_duration_lt_congr_23dogs_output_table.csv")
```
## First look - only 23 dogs that immediately passed manipulation check
##LL: continue adapting from here, use dogs.to.excl

scale covariates
```{r}
# Analysis of first look
first_look_data.23dogs<-first_look_data %>% 
  filter(!Subject %in% dogs.to.excl)
first_look_data.23dogs$z.trial<-scale(first_look_data.23dogs$trial)
first_look_data.23dogs$z.age<-scale(first_look_data.23dogs$age)

#manually dummy code and center looking_condition for random slope component 
first_look_data.23dogs$looking_condition.c<-as.factor(first_look_data.23dogs$looking_condition)
first_look_data.23dogs$looking_condition.c<-as.vector(scale(
  as.numeric(
    first_look_data.23dogs$looking_condition.c == levels(as.factor(
      first_look_data.23dogs$looking_condition.c
    ))[2]
  ),
  center = TRUE,
  scale = FALSE
))
```

```{r}
library(lme4)
#
mm2_fl<-glmer(first_look_cong ~ looking_condition+ transparent_screen+
            z.trial+z.age+sex+
            (1+z.trial+looking_condition.c|Subject), family=binomial, data=first_look_data.23dogs, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

```

```{R echo=FALSE, error=FALSE, warning=FALSE}
library(car)
col.full.fl2 <- lm(first_look_cong ~ looking_condition+ transparent_screen+ z.trial+z.age+sex, data = first_look_data.23dogs)
vif(col.full.fl2)
#no problem
```
Check model stability
```{r eval=FALSE, echo=FALSE}
m.stab.fl2 <- glmm.model.stab(model.res = mm2_fl)
m.stab.fl2$detailed$warnings
as.data.frame(round(m.stab.fl2$summary[1:6, -1], 2))

m.stab.plot(round(m.stab.fl2$summary[, -1], 2))
```

Model output
  + Coefficients
```{r}
round(summary(mm2_fl)$coefficients, 2)
```
Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (R function drop1 with argument 'test' set to "Chisq"). 

```{r}
drop1.mm2_fl=drop1(mm2_fl, test="Chisq")
round(drop1.mm2_fl,3)
```

confidence intervals

```{r}
boot.res.mm2_fl=boot.glmm.pred(model.res=mm2_fl, excl.warnings=T,	nboots=1000, para=F)
ci.res.mm2_fl<-round(boot.res.mm2_fl$ci.estimates, 2)
ci.res.mm2_fl
```

```{r}
save.image(file="goggles_workspace.RData")
```


### output table - first look

```{r}
model_table_fl.23dogs<- bind_cols(as.data.frame(summary(mm2_fl)$coefficients),
                             drop1.mm2_fl,
                             boot.res.mm2_fl$ci.estimates[1:6,],
                             m.stab.fl2$summary[1:6, -1]) %>% 
  select(Estimate, SE = `Std. Error`, Chi2 = LRT, df = npar, p = `Pr(Chi)`, LowerCI = X2.5., UpperCI = X97.5., min, max) %>%  
  mutate(across(.cols = c(p), ~ format(round(.x, 3), nsmall=3))) %>% 
  mutate(across(.cols = c(Estimate:Chi2), ~ format(round(.x, 2), nsmall=2))) %>% 
  mutate(across(.cols = c(LowerCI:max), ~ format(round(.x, 2), nsmall=2))) 
  # mutate(across(Chi2:p, ~replace_na(.x, "")))%>%
  # mutate(p=replace(p, p==0, "<.001"))
model_table_fl.23dogs
write.csv(model_table_fl.23dogs, file = "saves/mm2_first_look_23dogs_output_table.csv")
```

